A publishing infrastructure for AI-assisted academic authoring

### 2023-12-21 latex/manuscript.tex
latex: minor change in objectives section

This study has two objectives:
1) investigate how recently released large language models can reduce the time-consuming process of writing and revising scholarly manuscripts;
2) develop an approach that integrates these models into the Manubot publishing ecosystem to transparently suggest revisions to improve the quality of the original text.

>>>>

This study has two objectives:
1) investigate how recently released large language models can reduce the time-consuming process of writing and revising scholarly manuscripts;
2) develop an approach for incorporating these models into the Manubot publishing ecosystem to transparently suggest revisions to improve the quality of the original text.
